\section{Lecture 9 (April 3rd)}
\begin{thm}
(Cauchy theorem) Let $D$ be a simply connected domain and let $f$ be analytic on $D$. Then,
\[\int _{C}f(z)\;dz=0\]
for every simple closed contour $C$ in $D$. Note that the condition implies that $f$ is analytic on $\bar{D}$ for a bounded domain $D$. 
\end{thm}
\vspace{2ex}
\begin{rmk}
There are two cases for which Cauchy theorem is true. 
\begin{itemize}
\item[(i)] $D$ is simply connected and $\partial D$ is a simple closed contour
\item[(ii)] $D$ is multiply connected, $\partial D$ is a union of disjoint simple closed contour
then 
\[\int _{\partial D}f(z)\;dz=0\]
where $\partial D$ has a positive orientation.
\end{itemize}
The second one can be seen as a corollary of the first and can be proven as
\[\int _{-C}f(z)\;dz=-\int _{C}f(z)\;dz\]
and multiply connected domain can be seen as an amalgamation of a single one.
\end{rmk}
\vspace{2ex}
\begin{ex}
\begin{itemize}
\item[(i)] \[\int ^{\infty }_{0}\dfrac{\sin x}{x}\;dx\]
\item[(ii)] \[\int ^{\infty }_{0}\sin x^2\;dx\]
both of the above converge by the alterating series theorem. We can find these values using expressing them as analytic complex integrals. 
\end{itemize}
\end{ex}
\vspace{2ex}
\begin{ex}
Let $f(z)=e^{iz^2}$ (entire function). Let $C_{R}$ be a positively oriented contour given by one eighth on a circle with radius $R$. 
\begin{itemize}
\item[(i)] By the Cauchy theorem, 
\[\int_{C_{R}}e^{iz^2}\;dz=0\]
for all $R>0$
\item[(ii)] By parametrisation, 
\begin{align*}
\int _{C_{R}}e^{iz^2}\;dz=&\int _{\mathrm{I}}e^{iz^2}\;dz+\int _{\mathrm{II}}e^{iz^2}\;dz+\int _{\mathrm{III}}e^{iz^2}\;dz\\
=&\int _{0}^{R}e^{ix^2}\;dx+\int _{\mathrm{II}}e^{iz^2}dz-\int ^{R}_{0}\exp \Big[i\Big(xe^{\pi i/4}\Big)^2\Big]e^{\pi i/4}\;dx\\
=&\int ^{R}_{0}e^{ix^2}\;dx+\int _{\mathrm{II}}e^{iz^2}\;dz-e^{\pi i/4}\int^{R}_{0}e^{-x^2}\;dx
\end{align*}
At this point, take $R\rightarrow \infty $ and we have:
\[0=\int ^{\infty }_{0}e^{ix^2}\;dx-e^{\pi i/4}\int ^{\infty }_{0}e^{-x^2}\;dx\]
This implies that
\[\int ^{\infty }_{0}e^{ix^2}\;dx=\int ^{\infty }_{0}=e^{\pi i/4}\dfrac{\sqrt{\pi }}{2}\]
and finally
\[\int ^{\infty }_{0}\cos x^2\;dx=\dfrac{\sqrt{2}}{2}\dfrac{\sqrt{\pi }}{2}=\int ^{\infty }_{0}\sin x^2\;dx\]
\end{itemize}
\end{ex}
\vspace{2ex}
\begin{ex}
Consider an upper half hemisphere with outer radius $R$ and inner radius $\varepsilon $, $C_{\varepsilon ,R}$, which is positively oriented. Also, take $f(z)=e^{iz}/z$. Again, we have two methods:
\begin{itemize}
\item[(i)] By the Cauchy theorem,
\[\int _{C_{\varepsilon ,R}}f(z)\;dz=0\]
for every $0<\varepsilon <R<\infty $
\item[(ii)] By parametrisation, 
\[\int _{C_{\varepsilon ,R}}f(z)\;dz=\int _{\mathrm{I}}f(z)\;dz+\ldots +\int _{\mathrm{IV}}f(z)\;dz\]
By taking $\varepsilon \rightarrow 0^{+}$ and $R\rightarrow \infty $, we achieve
\[\int ^{\infty }_{0}\dfrac{\sin x}{x}\;dx=\dfrac{\pi }{2}\]
\end{itemize}
\end{ex}
\vspace{2ex}
\begin{thm}
(Cauchy Integral Formula) Let $f$ be analytic inside and on a POSCC $C$ then for every $z_0$ inside $C$, we have
\[f(z_0)=\dfrac{1}{2\pi i}\int _{C}\dfrac{f(z)}{z-z_0}\;dz\]
\end{thm}
\vspace{2ex}
\begin{proof}
Take any $\varepsilon >0$. We'll show that
\[\Big|f(z_0)-\dfrac{1}{2\pi i}\int _{C}\dfrac{f(z)}{z-z_0}\;dz\Big|<\varepsilon \]
Since $f$ is continuous at $z_0$ there is $\delta >0$ such that if $|z-z_0|<\delta $ then $|f(z)-f(z_0)|<\varepsilon $. Take $r<\delta $ and apply the Cauchy theorem to $f(z)/z-z_0$ on a positively oriented shell around $z_0$ with inner radius $r$. Then, the function is analytic with that shell and
\[0=\int _{C}\dfrac{f(z)}{z-z_0}\;dz-\int _{|z-z_0|=r}\dfrac{f(z)}{z-z_0}\;dz\]
where the right integral is evaluated contour clockwise. Then,
\begin{align*}
\int _{C}\dfrac{f(z)}{z-z_0}\;dz=&\int_{|z-z_0|=r}\dfrac{f(z)}{z-z_0}\;dz\\
=&\int _{|z-z_0|=r}\dfrac{f(z)-f(z_0)}{z-z_0}\;dz+\int _{|z-z_0|=r}\dfrac{f(z_0)}{z-z_0}\;dz
\end{align*}
We therefore arrive at the equality
\[\int _{C}\dfrac{f(z)}{z-z_0}\;dz-2\pi if(z_0)=\int _{|z-z_0|=r}\dfrac{f(z)-f(z_0)}{z-z_0}\;dz\]
and by applying the modulus function we have
\[\Big|\int_{C}\dfrac{f(z)}{z-z_0}\;dz-2\pi if(z_0)\Big|\leq \int _{|z-z_0|=r}\dfrac{\varepsilon }{r}|dz|=2\pi \varepsilon \]
dividing each side by $2\pi =|2\pi i|$ completes the proof. There are two ideas inside this proof: (1) the integral of $1/z-z_0$ and (2) the continuity of $f(z)$ at $z_0$. 
\end{proof}
\vspace{2ex}
\begin{rmk}
Let $D$ be a bounded simply connected domain whose boundary $\partial D$ is a closed contour. If $f$ is analytic on $\bar{D}=D\cup \partial D$, then
\[f(z)=\dfrac{1}{2\pi i}\int _{\partial D}\dfrac{f(\xi )}{\xi -z}\;d\xi \]
for all $z\in D$. Notice how the value of $f$ on $D$ is determined by its boundary values. From this, we have a power series representation of $f$. 
\end{rmk}
\vspace{2ex}

